\cvsection{Experience}
\begin{cventries}
  \cventry
    {Software Developer \& Security Researcher (Alternative Military Service)}
    {Mirageworks Inc.}
    {Seoul, S.Korea}
    {June. 2014 - Exp. Jan. 2016}
    {
      \begin{cvitems}
        \item {Military service, a research position collaborating with companies.}
%        \item {Implemented a virtualization solutions on Windows using Sandbox \& Watchdog, which developmented through API Hook, Virtual Disk, and Device Driver.}
        \item {Contributed to the development and continuous enhancement of the company's client-side/platform framework.}
        \item {Developed the windows client-side virtualization solution based on injecting and hooking skills (named as sandbox and watchdog), windows drivers, and virtual disk.}
        \item {Provided the company's own platform framework like c\# using c++.}
        \item {Managed program compatible with windows up-to-date version and programs running on windows, using reverse code engineering and debugging tools.}
%        \item {Implemented a military cooperation system which is web based real time messenger in Scala on Lift.}
%        \item {Improved functionality on military command and control system for incident response with Java Servlet.}
%        \item {Lead engineer on agent-less backtracking system that can discover client device's fingerprint(including public and private IP) independently of the Proxy, VPN and NAT.}
      \end{cvitems}
    }
  \cventry
    {Software Developer (Alternaative Military Service)}
    {Aircuve Inc.}
    {Seoul, S.Korea}
    {Jan. 2013 - May. 2014}
    {
      \begin{cvitems}
        \item {Military service, a research position collaborating with companies.}
        \item {Developed internet access management solutions on Windows.}
        \item {According to manager's policies, allow/block the network and packet using NDIS drivers.}
%        \item {Developed in Cocos2d-x an action puzzle game(Dragon Buster) targeting U.S. market. Implemented API server which is communicating with game client and In-App Store, along with two other team members who wrote the game logic, designed game graphics.}
%        \item {Won the 2nd prize in final evaluation.}
      \end{cvitems}
    }
  \cventry
    {Penetration Tester}
    {SAMSUNG Display}
    {S.Korea}
    {July. 2015 - Aug. 2015}
    {
      \begin{cvitems}
        \item {Conducted intranet penetration testing on SAMSUNG Display}
      \end{cvitems} 
    }
%  \cventry
%    {Software Engineer Trainee}
%    {Software Maestro (funded by Korea Ministry of Knowledge and Economy)}
%    {Seoul, S.Korea}
%    {Jul. 2012 - Jun. 2013}
%    {
%      \begin{cvitems}
%        \item {Performed research memory management strategies of OS and implemented in Python an interactive simulator for Linux kernel memory management.}
%      \end{cvitems}
%    }
\end{cventries}
