\cvsection{Extracurricular Activity}
\begin{cventries}
  \cventry
    {Member}
    {NULL@ROOT (Underground hacker group)}
    {S.Korea}
    {Dec. 2013 - PRESENT}
    {
      \begin{cvitems}
        \item {Participated on a lot of hacking competition and won a good award.}
        \item {Held several hacking competitions non-profit, just for honors.}
      \end{cvitems}
    }
  \cventry
    {Member}
    {CAT-Security (CERT in Catholic University)}
    {S.Korea}
    {Mar. 2009 - Feb. 2012}
    {
      \begin{cvitems}
        \item {Learned a lot about the security area and about skills for hacking}
        \item {Condected penetration testing commissioned by Catholic University}
        \item {Participated on a lot of hacking competition}
        \item {Hosted \& managed hacking festival 'Holy Shield' every years since 2010}
        \item {Trained that focus on RCE, Malware/Exploit analysis, and exploit technique based on UNIX}
      \end{cvitems}
    }
  \cventry
    {President at 2012}
    {KUCIS (Korea University Clubs of Information Security)}
    {S.Korea}
    {Feb. 2012 - Feb. 2013}
    {
      \begin{cvitems}
        \item {organized by KISA(Korea Internet \& Security Agency)}
        \item {Consist of over 40 security clubs of university, including Korea univ, Yonsei univ, KAIST etc.}
        \item {Planned several security seminars and lecture}
      \end{cvitems}
    }
  \cventry
    {Member}
    {MSP (Student developer support program, sponsored by Microsoft)}
    {Seoul, S.Korea}
    {Aug. 2011 - July. 2012}
    {
      \begin{cvitems}
        \item {Gained expertise in developments about Windows phone applications}
        \item {Origanized study groups, which studied about Windows OS}
      \end{cvitems}
    }
\end{cventries}
