\cvsection{Projects}
\begin{cventries}
  \cventry
    {teamname 'Weekend Surplus' at NULL@ROOT}
    {Following up 'Exploit-DB' in 2016 1st-Half}
    {S.Korea}
    {Jan. 2016 - PRESENT}
    {
      \begin{cvitems}
        \item {To find brand-new and critical vulnerability, I'm following up on Exploit-DB and latest trends.}
        \item {This project will run until June, and I have a plan to write several documents. Our Purpose is what to look forward in finding a new CVE this year.}
      \end{cvitems}
    }
  \cventry
    {teamname 'Weekend Surplus' at NULL@ROOT}
    {Making CTF problem solver using Triton}
    {S.Korea}
    {Jul. 2015 - Dec. 2015}
    {
      \begin{cvitems}
        \item {Using C/C++, Python, and PIN framework}
        \item {Triton is Dynamic-Symbolic-Excution(DSE) framework. We were trying to make a script of Triton's template to solve a CTF problem, for example, could we reach some vulnerability points automatically. By making and some trolling, I learned the basic concept of DSE, committed some modifying code, and wrote document about using Triton for CTF.}
        \item {https://github.com/JonathanSalwan/Triton}
      \end{cvitems}
    }
  \cventry
    {Personal project}
    {Writing document about Process Hacker}
    {S.Korea}
    {Jan. 2014 - PRESENT}
    {
      \begin{cvitems}
        \item {Using C, WinAPI, and MFC}
        \item {This project started just for fun. I was interested how Windows OS executes some PE programs, so I began analyze source code about Process Hacker. Although these days I unable to continue because of office work, however I do still analyze it step by step.}
      \end{cvitems}
    }

  \cventry
    {teamname 'MudTang'}
    {Making sandbox for malware analysis}
    {S.Korea}
    {Sep. 2012 - Dec. 2012}
    {
      \begin{cvitems}
        \item {Using C, WinAPI, and MFC}
        \item {Developed sandbox to detect malicious behavior. Analyzed several open-source sandboxes like cukcoo, defined malicious patterns in which malware was commonly use, and implemented function to detect malware using API hooking.}
        \item {It was a great opportunity for thinking about vaccines fundamentally and a way I can bypass detection of vaccine.}
      \end{cvitems}
    }
  \cventry
    {CAT-Security}
    {Implementing simple operating system}
    {S.Korea}
    {Apr. 2012 - Nov. 2012}
    {
      \begin{cvitems}
        \item {Using assembly and C}
        \item {There is no output to show something, but why I embraced this project because it made me fall deeply into the security area. In this project, my part was developing the boot-loader, Protect-Mode, and communications with hardware. Unfortunately, I didn't get to implement User-Mode because the project was overdue.}
        %\item {There is no output to show something, but why I embraced this project is it makes me falling in security area deeply. In this project, my part was developing boot-loader, Protect-Mode, and communications with hardware. Unfortunately, I didn't reach to implement User-Mode because project is overdue.} % have to check some grammer about this sentence.
      \end{cvitems}
    }

%  \cventry
%    {CAT-Security}
%    {Making PE-editor for referrence}
%    {S.Korea}
%    {Mar. 2011 - Jul. 2011}
%    {
%%      \begin{cvitems}
%        \item {Using C, WinAPI, and MFC}
%        \item {Blah Blah Blah}
%      \end{cvitems}
%    }
\end{cventries}
